Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-19 paper.tex
start
more

\section{Introduction}
Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008}
Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states. \cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, RN325} 
CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}

@@

The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere. \cite{Carlson1988thesis} 
A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{drsive_spectrum.png}
	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
		(a) Potential energy surface, (b) HDFG spectrum for $\Delta = 0.5$.}
	\label{fig:doubres_spec}
\end{figure}

>>>>

\section{Introduction}
Coherent multidimensional spectroscopy (CMDS) is a family of three and four wave mixing methods which form the optical analogue of multidimensional nuclear magnetic resonance (NMR) spectroscopy.\cite{RN103, Cho2008}
Multiresonant, four wave mixing CMDS experiments, first proposed by Oudar and Shen in 1980,\cite{RN307} directly probe coupling and correlations between different vibrational, electronic, and vibronic states. \cite{RN307, RN281, RN103, RN342, Cho2008, Dong2015, Ogilvie2019, Bonn2021, RN325} 
CMDS has resolved anharmonicities, ultrafast dynamics, and other intramolecular couplings in numerous systems. \cite{RN342, RN343, RN324, Czech2015, Gaynor2017, Ogilvie2019, RN325}

@@

The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega Q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (Q-\Delta)^2 +\hbar \omega_{eg}$, the A and B contributions can be easily evaluated using Franck-Condon and Herzberg-Teller integrals tabulated elsewhere. \cite{Carlson1988thesis} 
A simulated spectrum highlighting the contributions of these terms (\autoref{fig:doubres_spec}) on potential wells with $\Delta = 0.5$ using values listed in \autoref{T:hdfgvalues} dissects the $A$ and $B$ contributions to the DR-SIVE spectrum.
%stimulated hyper Raman spectrum -- relationship
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=3.375in]{drsive_spectrum.png}
	\caption{DR-HDFG $\gamma_{ijkl}$ spectrum for a simple two harmonic well system.
		(a) Potential energy surface, (b) HDFG spectrum for $\Delta = 0.5$.}
	\label{fig:doubres_spec}
\end{figure}
